Inferring the effective start dates of non-pharmaceutical interventions during COVID-19 outbreaks

### 2020-05-20 ms/ms.tex
revised biblio

% NatBib
\usepackage[numbers,super,sort&compress]{natbib}
%\usepackage[round,colon,authoryear]{natbib}
\renewcommand{\bibsection}{}
\renewcommand{\bibfont}{\small}

@@

\author[a]{Ilia Kohanovski}
\author[b,c]{Uri Obolski}
\author[a,*]{Yoav Ram}

\affil[a]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya 4610101, Israel}
\affil[b]{School of Public Health, Tel Aviv University, Tel Aviv 6997801, Israel}{
\affil[c]{Porter School of the Environment and Earth Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}

@@

\begin{multicols}{2}[\section*{References}]
\nolinenumbers
\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms}
\end{multicols}

@@

    \textbf{Figure S2. Posterior prediction check plots}

@@

\pagebreak

>>>>

% NatBib
\usepackage[super]{natbib}
%\usepackage[numbers,super,sort&compress]{natbib}
%\usepackage[round,colon,authoryear]{natbib}
\renewcommand{\bibsection}{}
%\renewcommand{\bibfont}{\small}

@@

\author[1]{Ilia Kohanovski}
\author[2,3]{Uri Obolski}
\author[1,a]{Yoav Ram}

\affil[1]{School of Computer Science, Interdisciplinary Center Herzliya, Herzliya 4610101, Israel}
\affil[2]{School of Public Health, Tel Aviv University, Tel Aviv 6997801, Israel}{
\affil[3]{Porter School of the Environment and Earth Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
\affil[a]{Corresponding author: yoav@yoavram.com}

@@

\section*{References}
\nolinenumbers
\bibliographystyle{Science}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms}

@@

    \textbf{Figure S3. Posterior prediction check plots}

@@
